Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-08 ipsj/paper.tex
Add Introduction

\affiliate{OSAKA}{Graduate School of Engineering Science, Osaka University}
\affiliate{NAGOYA}{Graduate School of Information Science, Nagoya University}
\affiliate{OKUMA}{OKUMA Corporation}

@@

%1
\section{Introduction}

@@

%3
\section{Proposed Framework}

@@

\subsubsection{Component Design of TLSF memory allocator}

@@

%4
\section{Evaluation}

%5
\section{Related Work}

%6
\section{Conclusion}

>>>>

\affiliate{OSAKA}{Graduate School of Engineering Science, Osaka University}
\affiliate{NAGOYA}{Graduate School of Informatics, Nagoya University}
\affiliate{OKUMA}{OKUMA Corporation}

@@

%1
\section{Introduction}
\label{sec:Introduction}

The Internet of Things (IoT) is an essential next evolutionary step for the Internet \cite{par:IoTComputing} in which various items and platforms, for example, wearable devices and smart devices, will be connected via the Internet to further enrich people's lives.
The IoT uses embedded systems such as data sensors and controlling actuators as elemental constituents, and they must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

Complex and large-scale software systems can be developed efficiently by using component-based techniques \cite{par:Crnkovic}, \cite{par:CBD}.
Component-Based Development (CBD) is a design technique that can be applied to reusable software development.
Verification of component-based systems has been extensively researched \cite{par:Blaming}, \cite{par:Verification}.
Individual component diagrams enable the visualization of an entire system.
In addition, component-based systems are flexible with regard to extensibility and specification changes.
The TOPPERS embedded component system (TECS) \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach} are typical CBD tools for embedded systems.

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most embedded software are programmed in C language.
However, development in C language results in large code size, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because it is relatively easy to reuse scripts.

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.

This paper proposes an extended framework of mruby on TECS that can be applied to embedded network software development for IoT devices.
In the proposed framework, a component-based TCP/IP protocol stack, TINET+TECS \cite{par:TINET+TECS}, is comprised, and it is possible to utilize TINET function from mruby programs.

TINET is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET comprises many complex source codes, i.e., it contains many files and defines many macros, which can be problematic for software developers seeking to maintain, extend, and analyze the software.
TINET+TECS is a componentized TIENT with TECS to improve the configurability and scalability of TCP/IP software.

In addition, this paper proposes a component-based dynamic memory allocator, TLSF+TECS. 
TLSF is a dynamic memory allocator for real-time systems, which can always run with $O(1)$ and improve memory usage efficiency by deviding memory blocks in two stages.
In the current version of TLSF, memory contention may occur when multiple threads run at the same time.
TLSF+TECS is a componentized TLSF memory allocator, which can be thread-safe allocator because each component has its own heap area.

{\bf Contributions}: The proposed framework provides the following contributions.
\begin{enumerate}
\item {\bf :}
\item {\bf :}
\item {\bf :}
\item {\bf :}
\end{enumerate}

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., mruby, TECS, and mruby on TECS.
Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

%3
\section{Proposed Framework}
\label{sec:Proposed Framework}

@@

\subsubsection{Component Design of TLSF}

@@

%4
\section{Evaluation}
\label{sec:Evaluation}

%5
\section{Related Work}
\label{sec:Related Work}

%6
\section{Conclusion}
\label{sec:Conclusion}
